Disparity through time figures

### 2018-02-05 analyses/05-figure-dtt.Rmd
Make error bars more transparent and wider

beck_s <- 
  beck_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Stratigraphy") +
  theme(plot.title = element_text(size = 14, hjust = 0.5)) +
  annotate("text", x = 75, y = 0.15, label = "Beck2014")

beck_d <- 
  beck_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Duration") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

beck_n <- 
  beck_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  ggtitle("Number") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

@@

brusatte_s <- 
  brusatte_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 140, y = 0.15, label = "Brusatte2014")

brusatte_d <- 
  brusatte_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

brusatte_n <- 
  brusatte_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

@@

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 120, y = 0.15, label = "Bapst2016")

bapst_d <- 
  bapst_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

bapst_n <- 
  bapst_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

@@

wright_s <- 
  wright_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 440, y = 0.15, label = "Wright2017")

wright_d <- 
  wright_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  scale_x_reverse(limits = c(470, 370),
                  breaks = c(seq(470, 370, by = -100)))

wright_n <- 
  wright_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

@@

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8) +
  annotate("text", x = 165, y = 0.15, label = "Bapst2016")

bapst_d <- 
  bapst_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

bapst_n <- 
  bapst_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 1, alpha = 0.8)

>>>>

beck_s <- 
  beck_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3) +
  ggtitle("Stratigraphy") +
  theme(plot.title = element_text(size = 14, hjust = 0.5)) +
  annotate("text", x = 75, y = 0.15, label = "Beck2014")

beck_d <- 
  beck_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3) +
  ggtitle("Duration") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

beck_n <- 
  beck_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3) +
  ggtitle("Number") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

@@

brusatte_s <- 
  brusatte_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3) +
  annotate("text", x = 140, y = 0.15, label = "Brusatte2014")

brusatte_d <- 
  brusatte_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3)

brusatte_n <- 
  brusatte_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3)

@@

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3) +
  annotate("text", x = 120, y = 0.15, label = "Bapst2016")

bapst_d <- 
  bapst_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3)

bapst_n <- 
  bapst_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3)

@@

wright_s <- 
  wright_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3) +
  annotate("text", x = 440, y = 0.15, label = "Wright2017")

wright_d <- 
  wright_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3) +
  scale_x_reverse(limits = c(470, 370),
                  breaks = c(seq(470, 370, by = -100)))

wright_n <- 
  wright_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3)

@@

bapst_s <- 
  bapst_base +
  geom_point(data = strat2, size = 2, alpha = 0.8) +
  geom_errorbar(data = strat2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3) +
  annotate("text", x = 165, y = 0.15, label = "Bapst2016")

bapst_d <- 
  bapst_base +
  geom_point(data = duration2, size = 2, alpha = 0.8) +
  geom_errorbar(data = duration2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3)

bapst_n <- 
  bapst_base +
  geom_point(data = number2, size = 2, alpha = 0.8) +
  geom_errorbar(data = number2, aes(ymin = relative.lwr, ymax = relative.upr), width = 2, alpha = 0.3)
